### 2019-07-08 ms.tex
Minor fig edits.

\begin{figure}
% to be removed before submission
\includegraphics[width = 0.7\textwidth]{figures/idn_both_cv12_preds.png}
\caption{{\bf Input incidence data and predicted incidence maps. } 
The incidence (log10) data (top), predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Indonesia. The values plotted for areas with no polygon data are the means across all cross-validation folds.
}
\label{predobsmapidn}
\end{figure}

\begin{figure}
% to be removed before submission
\includegraphics[width = 0.7\textwidth]{figures/sen_both_cv12_preds.png}
\caption{{\bf Input incidence data and predicted incidence maps. } 
The incidence (log10) data, predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Senegal.
}
\label{predobsmapsen}
\end{figure}

>>>>

\begin{figure}
% to be removed before submission
\includegraphics[width = 0.7\textwidth]{figures/idn_both_cv12_preds.png}
\caption{{\bf Input incidence data and predicted incidence maps. } 
The incidence (log10) data (top), predicted log10 incidence from the prevalence GP model for spatially sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Indonesia. The values plotted for areas with no polygon data are the means across all cross-validation folds.
}
\label{predobsmapidn}
\end{figure}

\begin{figure}
% to be removed before submission
\includegraphics[width = 0.7\textwidth]{figures/sen_both_cv12_preds.png}
\caption{{\bf Input incidence data and predicted incidence maps. } 
The incidence (log10) data, predicted log10 incidence from the prevalence GP model for spatially sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Senegal.
}
\label{predobsmapsen}
\end{figure}

\begin{figure}
% to be removed before submission
\includegraphics[width = 1.1\textwidth]{figures/mdg_both_cv12_preds.png}
\caption{{\bf Input incidence data and predicted incidence maps. } 
The incidence (log10) data, predicted log10 incidence from the prevalence GP model for spatially sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Senegal.
}
\label{predobsmapsen}
\end{figure}
